Introducing Statistical Design of Experiments to SPARQL Endpoint Evaluation

### 2013-05-10 exp1/iswc2013.tex
bothersome questions
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@565 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

To this end, the following questions must be asked:
\begin{enumerate}
\item Are there factors that cover all realistic features?
\item If not, are they adequately covered by randomization?
\item If so, would the variance resulting from randomization obscure
  factors that could provide clues that the levels are wrongly set?
\item By carefully examining interactions with ``Implement'', are
  there any that are unaccounted for, and that could point out wrongly
  set levels?
\end{enumarate}
